### 2015-11-30 Manuscript/BiologyLetters/Supplementary/ESM_1.tex
Final minor typos edits

\subsubsection{Ross Mounce}
We accessed Ross Mounce's GitHub repository (\texttt{https://github.com/rossmounce}) on the 11th of June 2015 and downloaded every 601 matrix.
We then ran a shell script to select only the matrices that had any text element that match with one of the search terms.
% LINK WHICH SHELL SCRIPT
To make the matrix selection more thorough, we ignored the keywords case as well as the latin suffix (\textit{ia}, \textit{ata}, \textit{ea}, and \textit{a}).

>>>>

\subsubsection{Ross Mounce}
We accessed Ross Mounce's GitHub repository (\texttt{https://github.com/rossmounce}) on the 11th of June 2015 and downloaded all 601 matrix.
We then ran a shell script to select only the matrices that had any text element that match with one of the search terms.
% LINK WHICH SHELL SCRIPT
To make the matrix selection more thorough, we ignored the keywords case as well as the latin suffix (\textit{ia}, \textit{ata}, \textit{ea}, and \textit{a}).
